### 2014-03-09 src/analysis.Rnw
update

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              NA)))))))
df$strat <- with(df,
    ifelse(grepl('perunit', strategy), 'xpercent',
      ifelse(grepl('op',strategy), 'opsel',
        ifelse(grepl('one',strategy), 'oneperelm',
          ifelse(grepl('elem',strategy), 'loc', 'other'
            )))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
@
\end{figure*}
\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
@
\end{figure*}
\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\end{figure*}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames
@

@@

% ----------------------------------------------------------------------
\subsection{Mutant Clustering}
To be added later.
% IGNORED FROM HERE.
\if 0
\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.1,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
@

\subsection{Correlation Analysis}

$ \mu\{ M_{all}| M_{sample} \} = 0 + \beta_1 \times M{sample}  $

The interesting part is (1) the $\beta_1$ coefficient which tells how much we must multiply the  sampled/selected score to get original score, and $R^2$ which tells us how close the score is.

\subsubsection{sdl.mut.avg and mut.avg}

% <<>>=
% c <- cor(subset(m, select=c(sdl.mut.avg, mut.avg)) , method="kendall", use="pairwise")['sdl.mut.avg', 'mut.avg']
% d <- cor(subset(m, select=c(lrnd.mut.avg, mut.avg)) , method="kendall", use="pairwise")['lrnd.mut.avg', 'mut.avg']
% @
$ \mu_\{M_{all} | M_{sdl}\} = Sexpr{sdl.est} \times M_{sdl} \text{ : } R^2 = Sexpr{sdl.r} \text{,} \tau_{\beta} = Sexpr{c}$

\subsubsection{lrnd.mut.avg and mut.avg}

$ \mu_\{M_{all} | M_{rnd}\} = Sexpr{rnd.est} \times M_{rnd} \text{ : } R^2 = Sexpr{rnd.r} \text{,} \tau_{\beta} = Sexpr{d}$

\subsection{Regression Analysis}
The next question we will tackle is if there exist a difference at all between SDL mutagen and the random sampling. We can perform two statistical tests to answer this question. For the first, we run a simple paired t-test.

%<<>>=
%s <- t.test(lrnd.mut.avg, sdl.mut.avg, paired=T)
%@

The paired t-test failed to sufficient difference between the two distributions with a two-sided p-value of Sexpr{s.p.value}. That is, we do not have sufficient evidence to conclude that the two distributions are different.

The second approch is convoluted (I am a little unclear here.). We try to predict the original mutation score using the mutation score from both sdl and random sampling.
Our full model is

$ \mu_\{M_{all} | M_{sdl}, M_{rnd}\} = 0 + \beta_1 {sdl} + \beta_2 M_{rnd} + \beta_3 M_{sdl} M_{rnd}  $
\begin{small}
% <<results='asis'>>=
% s <- subset(m, select=c(mut.avg,sdl.mut.avg))
% s$type <- 'sdl'
% colnames(s) <- c('mut', 'sample', 'type')
% r <- subset(m, select=c(mut.avg,lrnd.mut.avg))
% r$type <- 'rnd'
% colnames(r) <- c('mut', 'sample', 'type')
% all <- rbind(s, r)
% fm <- with(all, lm(mut ~ sample + type + sample:type))
% sm <- anova(fm)
% print(xtable(sm,caption="My caption"), size="\\small")
% @
\end{small}

We see that both type and sample:type are non-significant for predicting the final model, and sequentially removing them does not change the effectiveness. Hence, the techniques random sampling and statement deletion operator do not have any difference.

\begin{figure*}[t]
% <<tplots, fig.width=5, fig.height=5, out.width='.45\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
% t_f <- sdl.time~lrnd.time
% plot(t_f, main='SDL ~ RND',pch='*')
% abline(lm(t_f), col='red')
% detach(m)
% @
\caption{Time}
\label{fig:caddrm}
\end{figure*}

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/original.pdf}
\caption{Subsumption Original}
\label{fig:subsumptiono}
\end{figure*}[t]

\begin{figure*}[t]
\includegraphics[totalheight=6cm]{fig/randoop.pdf}
\caption{Subsumption Randoop}
\label{fig:subsumptionr}
\end{figure*}[t]
%% END HERE
\fi

>>>>

df <-  subset(stats.df, r.square>=0.9 & (sd.reduction * 2) < mutant.reduction)
df$sqr <- 1 - df$r.square
df$mult <- 1 - df$score.multiplier
df$type <- with(df, as.factor(
      ifelse(grepl('line',operator), 'line',
        ifelse(grepl('block',operator), 'block',
        ifelse(grepl('method',operator), 'method',
          ifelse(grepl('class',operator), 'class',
            ifelse(grepl('project',operator), 'project',
              NA)))))))
df$strat <- with(df,
    ifelse(grepl('perunit', strategy), 'xpercent',
      ifelse(grepl('op',strategy), 'opsel',
        ifelse(grepl('one',strategy), 'oneperelm',
          ifelse(grepl('elem',strategy), 'loc', 'other'
            )))))
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(size=sqr, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. The sqr represents (1-$R^2$), i.e smaller is good. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\label{fig:fullimgsize}
\end{figure*}
\begin{figure*}[t]
<<op.all.2,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=type))
@
\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. }
\end{figure*}

\begin{figure*}[t]
<<op.all.4,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
ggplot(df, aes(mutant.reduction, sd.reduction)) + geom_point(aes(shape=strat, color=mult))
@
\caption{The mean reduction of mutants vs its standard deviation. Only those observations with $R^2 > 0.9$ and $2\times $ standard deviation > mean reduction is shown here. The color represents the (1-multiplier) to the sampled mutation score to get final score }
\end{figure*}

\begin{figure*}[t]
<<op.all.3,fig.width=10, fig.height=5, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
dfd <- subset(df, !(strategy %in% c('op','opsel')) )
ggplot(dfd, aes(sd.reduction, mutant.reduction)) + geom_point(aes(shape=type, color=sqr)) + facet_wrap(~strategy) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
@
\label{fig:fullimgshape}
\end{figure*}
<<opsel>>=
stats.op <- subset(stats.rest, grepl('^(op|TSDL)', operator))
o.stats.sel.op <- subset(o.f(stats.op), select=sel.colnames)
r.stats.sel.op <- subset(r.f(stats.op), select=sel.colnames)
stats.rest <- subset(stats.rest, !grepl('^(op|TSDL)', operator))
colnames(o.stats.sel.op) <- new.colnames
colnames(r.stats.sel.op) <- new.colnames
@

@@

% ----------------------------------------------------------------------
\subsection{Mutant Clustering}
To be added later.

### 2014-03-09 src/results.Rnw
update

\section{Results}
\label{sec:results}
Our analysis of results suggests that different kinds of operator selection criterias can actually provide better reduction in mutants while not reducing the approximatin accuracy below acceptable limits.

>>>>

\section{Results}
\label{sec:results}
The first observation from our different kinds of random sampling is that the standard deviation tends to increase with the increase in mutation reduction. While this in itself is not unexpected, what is unexpected is the difference in the increase in standard deviation between different kinds of sampling techniques. Our observations suggests that random sampling based on the entire project has a much lower growth of standard deviation (and hence higher stability of results) than sampling in lower scopes. Further, we also observe that the rate of increase in standard deviation actually increases as we go into more finer scopes such as class, method and line, with line having the largest increase in standard deviation.

Further, looking at the reduction of mutants in Figure~\ref{fig:fullimgshape} and Figure~\ref{fig:fullimgsize}, we see that the x\% selection strategy is generally the best strategy, and it is generally best to stick with random selection from the entire project. This too is perhaps not unexpected, since sampling from the entire population rather than its elements should provide a better correlation with the final score.

Our analysis of results suggests that different kinds of operator selection criterias can actually provide better reduction in mutants while not reducing the approximatin accuracy below acceptable limits.
